---
title: "Report on Stats Anxiety"
author: "Dale"
date: "December 8, 2015"
output: pdf_document
bibliography: stars.bib
csl: apa.csl
---

We used the following add-on packages to perform the analyses and create the graphics.

```{r message=FALSE}
library("dplyr")   # data processing
library("tidyr")   # data reshaping
library("ggplot2") # plotting
```

Students from years 1, 2, and 3 were given the STARS statistical anxiety rating scale by @cruise_et_al_1985.

```{r, echo=FALSE, warning=FALSE}
scales <- read.csv("subscales.csv", stringsAsFactors = FALSE)

stars_wide <- read.csv("stars.csv", stringsAsFactors = FALSE)

stars <- stars_wide %>% gather(item_id, score, I01:I51)

stars_sub <- inner_join(scales, stars, "item_id")

## calculate subscale means per student_id and year
stars_means <- stars_sub %>%
   group_by(student_id, year, subscale) %>%
   summarise(mscore = mean(score))
```

Descriptive statistics for the subscales are below:

```{r, echo = FALSE, results = 'asis'}
dstats <- stars_means %>%
  group_by(subscale) %>%
  summarise(m = mean(mscore, na.rm = TRUE),
            med = median(mscore, na.rm = TRUE),
            sdev = sd(mscore, na.rm = TRUE))
knitr::kable(dstats)
```

```{r, echo = FALSE}
max_anx <- max(dstats$m)
highest <- dstats$subscale[dstats$m == max_anx]
```

Students exhibited greatest anxiety on the `r highest` subscale, with a mean anxiety rating of `r round(max_anx, 2)`.

# Plot

Here is a plot of the results by year:

```{r, echo = FALSE, warning = FALSE}
ggplot(stars_means, aes(subscale, mscore, color = subscale)) +
    geom_jitter(alpha = .7) +
    geom_violin(aes(fill = subscale), alpha = .2) +
    stat_summary(fun.y = 'median', geom = "point", size = 5) +
    coord_flip() + 
    facet_wrap(~year) +
    guides(color = FALSE, fill = FALSE)
```